Untitled

### 2023-12-27 code/analysis_Redo.Rmd
harmonizing color schemes

ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)
```

## Resources to support utilization

@@

df.util <- dfc %>% 
  inner_join(uds.sites.full %>% 
             filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
              #filter(`Location Setting` %in% c("All Other Clinic Types","School")) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year) %>% 
              summarise(Sites = n_distinct(`Site Name`), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)) %>% 
                mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar)), by = c("BHCMIS ID","Year")) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Staff, #Assets, 
         Sites.y, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
         Pct.NHA:Pct.COM)

@@

  df.temp <- df.util[,c(1:9, j, 12:ncol(df.util))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp  , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.util <- rbind(did.util, outcomes$coeftable)
}

@@

p1 <- df.util %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Staff:Sites.y) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Staff:Sites.y) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.util) %>%

@@

@@

## Broken down by components
```{r}
# 
# df.core <- dfc %>% 
#   mutate( MCD = Total * Pct.MCD / 100,
#          None = Total * Pct.None / 100,
#          MCR = Total * Pct.MCR / 100,
#          COM = Total * Pct.COM / 100,
#          
#          crc.rate = crc.rate * 100, 
#          pap.rate = pap.rate * 100, 
#          childbmi.rate = childbmi.rate * 100, 
#          adultbmi.rate = adultbmi.rate * 100, 
#          htn.rate = htn.rate * 100, 
#          dm.rate = dm.rate * 100) %>% 
#   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
#          MCD:COM, 
#          crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
#          Liquidity:NetWorth, 
#          Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman) 
#   
# 
# 
# 
# did.core <- c(0, 0, 0, 0)
# 
# for (j in 10:23){
#   
#   df.temp <- df.core[,c(1:9, j, 24:ncol(df.core))]
#   colnames(df.temp)[10] <- "Outcome"
#   outcomes <- did2s(
#       data = df.temp, 
#       yname = "Outcome", 
#       treatment = "Tx",
#         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , 
#         second_stage = ~ i(Tx, ref = FALSE),
#         cluster_var = "STATE",
#       verbose = FALSE
#     )
#   
#   did.core <- rbind(did.core, outcomes$coeftable)
#   
#   
# }
# 
# 
# did.core <- did.core[-1,]
# rownames(did.core) <- NULL
#

# 
# df.core %>% 
#   mutate(Post = ifelse(year.rel >= 0, 1, 0), 
#          Treated = ifelse(Att > 0, 1, 0)) %>% 
#   group_by(Post, Treated) %>% 
#   select(MCD:NetWorth) %>% 
#   summarise_all(mean.nas) %>% 
#   # summarise(Total = mean(Total, na.rm = TRUE), 
#   #           Quality = mean(Qcomp, na.rm = TRUE), 
#   #           Finances = mean(Altman, na.rm = TRUE)) %>% 
#   pivot_longer(cols = MCD:NetWorth) %>% 
#   mutate(value = round(value, 2)) %>% 
#   #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
#   pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
#   mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
#   cbind(did.core) %>% 
#    select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
#   mutate(Estimate = round(Estimate, 2), 
#          `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
#          `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
#   rename(Outcome = name) %>% 
#   select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
#   kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
#   kable_styling(latex_options = c("striped")) %>%
#   pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
#   add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))
# 
#

@@

p2 <- ggarrange(
  event_study(data = df.select.stint, 
  yname = "Complexity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") + xlab("Year Relative to Competitive Shock")  + ylab("Prevalence"), 
event_study(data = df.select.stint, 
  yname = "Intensity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity") + xlab("Year Relative to Competitive Shock") + ylab("Visits"), common.legend = TRUE ) 
p2

@@

@@

@@

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

>>>>

ggsave(filename = "Picture3ah.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0, width = 17, height = 9)

p0.simple <- ggarrange(
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 2, legend = F) 
p0.simple

ggsave(filename = "Picture3ahSimple.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p0.simple, width = 17, height = 9)

## Resources to support utilization, capacity

@@

df.util <- dfc %>% 
  inner_join(uds.sites.full %>% 
             filter(`Location Setting` %in% c("All Other Clinic Types","School") | is.na(`Location Setting`)) %>% 
              #filter(`Location Setting` %in% c("All Other Clinic Types","School")) %>% 
              mutate(Type.num = ifelse(`Location Type` == "Seasonal", 0.33, 
                                ifelse(`Location Type` == "Mobile Van", 0.66, 1)), 
                     Schedule = ifelse(`Operational Schedule` == "Full-Time", 1, 
                                ifelse(`Operational Schedule` == "Part-Time", 0.5, 0)),
                     Calendar = ifelse(`Calendar Schedule` == "Year-Round", 1,
                                ifelse(`Calendar Schedule` == "Seasonal", 0.5, 0))) %>% 
              group_by(`BHCMIS ID`, Year) %>% 
              summarise(Sites = n_distinct(`Site Name`), Mean.Hours = mean(Access, na.rm = TRUE), Total.Hours = sum(Access, na.rm = TRUE), 
                        Perminance = sum(Type.num, na.rm = TRUE), Schedule = sum(Schedule, na.rm = TRUE), Calendar = sum(Calendar, na.rm = TRUE)) %>% 
                mutate(Sites = ifelse(is.na(Sites), 0, Sites), 
         Mean.Hours = ifelse(is.na(Mean.Hours), 0, Mean.Hours), 
         Total.Hours = ifelse(is.na(Total.Hours), 0, Total.Hours), 
         Perminance = ifelse(is.na(Perminance), 0, Perminance), 
         Schedule = ifelse(is.na(Schedule), 0, Schedule), 
         Calendar = ifelse(is.na(Calendar), 0, Calendar)), by = c("BHCMIS ID","Year")) %>% 
  mutate(logPatsPerStaff = log(Total / Staff)) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Staff, #Assets, 
         Sites.y, #HIV.prev:Hypertension.care, pap.denom, crc.denom, adultbmi.denom, childbmi.denom, htn.denom, dm.denom,#MCD:COM, 
         logPatsPerStaff, 
         Pct.NHA:Pct.COM)

@@

  df.temp <- df.util[,c(1:9, j, 13:ncol(df.util))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp  , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )
  did.util <- rbind(did.util, outcomes$coeftable)
}

@@

p1 <- df.util %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Staff:logPatsPerStaff) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Staff:logPatsPerStaff) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.util) %>%

@@

did2s(
      data = dfc %>% mutate(outcome = log(Total / Staff)) %>% filter(outcome < 8 & !is.infinite(outcome)), 
      yname = "outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "STATE",
      verbose = TRUE
    )

exp(0.042076)
exp(0.19)

hist((dfc$Total / dfc$Staff))
summary(log(dfc$Total / dfc$Staff))

p14 <- event_study(data = dfc %>% mutate(outcome = log(Total / Staff)) %>% filter(outcome < 10),
  yname = "outcome", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>%
  #mutate(estimate = exp(estimate), std.error = exp(std.error)) %>% 
  filter(abs(term) <= 5) %>%
  filter(estimator == "Gardner (2021)") %>%
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Event Study - Effects of Competitive Shock on log Ratio of Patients Per Staff Member") + xlab("Year Relative to Competitive Shock") + ylab("log Patients")

p14

ggsave(filename = "Picture14.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p14, width = 17, height = 9)

@@

## Broken down by components
```{r}
# 
# df.core <- dfc %>%
#   mutate( MCD = Total * Pct.MCD / 100,
#          None = Total * Pct.None / 100,
#          MCR = Total * Pct.MCR / 100,
#          COM = Total * Pct.COM / 100,
# 
#          crc.rate = crc.rate * 100,
#          pap.rate = pap.rate * 100,
#          childbmi.rate = childbmi.rate * 100,
#          adultbmi.rate = adultbmi.rate * 100,
#          htn.rate = htn.rate * 100,
#          dm.rate = dm.rate * 100) %>%
#   select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE,
#          MCD:COM,
#          crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate,
#          Liquidity:NetWorth,
#          Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)
# 
# 
# 
# 
# did.core <- c(0, 0, 0, 0)
# 
# for (j in 10:23){
# 
#   df.temp <- df.core[,c(1:9, j, 24:ncol(df.core))]
#   colnames(df.temp)[10] <- "Outcome"
#   outcomes <- did2s(
#       data = df.temp,
#       yname = "Outcome",
#       treatment = "Tx",
#         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless | ID + Year ,
#         second_stage = ~ i(Tx, ref = FALSE),
#         cluster_var = "STATE",
#       verbose = FALSE
#     )
# 
#   did.core <- rbind(did.core, outcomes$coeftable)
# 
# 
# }
# 
# 
# did.core <- did.core[-1,]
# rownames(did.core) <- NULL
# 
# 
# 
# df.core %>%
#   mutate(Post = ifelse(year.rel >= 0, 1, 0),
#          Treated = ifelse(Att > 0, 1, 0)) %>%
#   group_by(Post, Treated) %>%
#   select(MCD:NetWorth) %>%
#   summarise_all(mean.nas) %>%
#   # summarise(Total = mean(Total, na.rm = TRUE),
#   #           Quality = mean(Qcomp, na.rm = TRUE),
#   #           Finances = mean(Altman, na.rm = TRUE)) %>%
#   pivot_longer(cols = MCD:NetWorth) %>%
#   mutate(value = round(value, 2)) %>%
#   #filter(name %in% c("Total", "Qcomp", "Altman")) %>%
#   pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>%
#   mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>%
#   cbind(did.core) %>%
#    select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>%
#   mutate(Estimate = round(Estimate, 2),
#          `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""),
#          `% Change` = round(Estimate / `1_0` * 100, 1)) %>%
#   rename(Outcome = name) %>%
#   select(Outcome:Estimate, `95% CI`, `% Change`) %>%
#   kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>%
#   kable_styling(latex_options = c("striped")) %>%
#   pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>%
#   add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

@@

p2 <- ggarrange(
  event_study(data = df.select.stint, 
  yname = "Complexity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Complexity") + xlab("Year Relative to Competitive Shock")  + ylab("Prevalence"), 
event_study(data = df.select.stint, 
  yname = "Intensity", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold'))+ 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Intensity") + xlab("Year Relative to Competitive Shock") + ylab("Visits"), common.legend = TRUE, legend = F) 
p2

@@

ggsave(filename = "Picture4.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p2, width = 17, height = 9)

@@

ggsave(filename = "Picture5.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = pm, width = 17, height = 9)
```

@@

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

zp4 <- event_study(data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")
